A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-20 tex/main.tex
Add boxplot visualisation.
Also: improve the colormap for the median plots.

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies}
    \label{fig:fixation_heatmap_std}
\end{figure}

@@

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_noise.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies (with noise)}
    \label{fig:fixation_heatmap_std}
\end{figure}

@@

Figure~\ref{fig:histograms_median_fixation_rates_std}
and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of the
fixation rates for all strategies.

@@

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_std.pdf}
    \caption{Median rank of players against population size}
    \label{fig:ranks_v_size_standard}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \includegraphics[width=\textwidth]{../img/median_rank_vs_population_size_noisy.pdf}
    \caption{Median  rank of players against population size with noise}
    \label{fig:ranks_v_size_noisy}
\end{figure}

>>>>

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Pairwise fixation probabilities of all strategies}
    \label{fig:fixation_heatmap_std}
\end{figure}

@@

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{../img/fixation_heatmap_14_noise.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Pairwise fixation probabilities of all strategies (with noise)}
    \label{fig:fixation_heatmap_std}
\end{figure}

@@

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_boxplot_2_std.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_4_std.pdf}
        %\caption{\(N=4\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_6_std.pdf}
        %\caption{\(N=6\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_boxplot_8_std.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_10_std.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_12_std.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_boxplot_14_std.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies}
    \label{fig:fixation_boxplot_std}
\end{figure}

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_boxplot_2_noise.pdf}
        \caption{\(N=2\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_4_noise.pdf}
        %\caption{\(N=4\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_6_noise.pdf}
        %\caption{\(N=6\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_boxplot_8_noise.pdf}
        \caption{\(N=8\)}
    \end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_10_noise.pdf}
        %\caption{\(N=10\)}
    %\end{subfigure}%

    %\begin{subfigure}[t]{\textwidth}
        %\centering
        %\includegraphics[width=\textwidth]{../img/fixation_boxplot_12_noise.pdf}
        %\caption{\(N=12\)}
    %\end{subfigure}%

    \begin{subfigure}[t]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../img/fixation_boxplot_14_noise.pdf}
        \caption{\(N=14\)}
    \end{subfigure}%
    \caption{Fixation probabilities of all strategies (with noise)}
    \label{fig:fixation_boxplot_std}
\end{figure}

Figure~\ref{fig:histograms_median_fixation_rates_std}
and~\ref{fig:histograms_median_fixation_rates_noise} show the distribution of
the median fixation rates for all strategies.

@@

\begin{figure}[!hbtp]

    \centering
    \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_std.pdf}
    \caption{Standard}
    \label{fig:ranks_v_size_standard}
    \end{subfigure}%
    ~
    \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[height=.9\textheight]{../img/median_rank_vs_population_size_noisy.pdf}
    \caption{Noise}
    \label{fig:ranks_v_size_noisy}
    \end{subfigure}
    \caption{Median rank of players against population size}

\end{figure}
